First Order Logic of Sparse Random Hyper-Graphs

### 2019-10-24 Article.tex

\begin{document}
\begin{abstract}
	We consider a finite relational vocabulary $\sigma$ with
    a first order theory $T$ written in $\sigma$ 
    composed of symmetry and 
    anti-reflexivity axioms. We define a binomial random model of finite 
    $\sigma$-structures that satisfy $T$ and show that first order properties have well defined asymptotic probabilities in the sparse 
    case. It is also shown that those limit probabilities are well-behaved with
    respect to some parameters that represent edge densities. 
    An application of these results to the problem of random Boolean 
    satisfability is presented afterwards. 
    We show that there is no first order property of $k$-CNF formulas
    that implies unsatisfability and holds for almost all typical 
    unsatisfable formulas when the number of clauses is linear.

@@

A (relational) vocabulary $\sigma$ is a collection of
relation symbols $(R_1,\dots, R_m,\dots)$
where each relation symbol has associated a natural number called its arity.
.\par

A ($\sigma$-)structure $\mathfrak{A}$ is composed of (1)
a set $A$, called the universe of $\mathfrak{A}$, and sets of tuples 
$R_i^{\mathfrak{A}}\subseteq A^{a_i}$ for all relation symbols 
$R_i$ in $\sigma$, where $a_i$ is the arity of $R_i$.  
A structure is called finite if its universe is a finite set.

>>>>

\begin{document}
\begin{abstract}
	We consider a finite relational vocabulary $\sigma$
	and a first order theory $T$ for $\sigma$ 
    composed of symmetry and 
    anti-reflexivity axioms. We define a binomial random model of finite 
    $\sigma$-structures that satisfy $T$ and show that first order properties have 
    well defined asymptotic probabilities in the sparse 
    case. It is also shown that those limit probabilities are well-behaved with
    respect to some parameters that represent edge densities. 
    An application of these results to the problem of random Boolean 
    satisfability is presented afterwards. 
    We show that there is no first order property of $k$-CNF formulas
    that implies unsatisfability and holds for almost all typical 
    unsatisfable formulas when the number of clauses is linear.

@@

A (relational) vocabulary $\sigma$ is a collection of
relation symbols $(R_1,\dots, R_m,\dots)$
where each relation symbol $R_i$ has associated a natural $a_i$
number called its arity.
.\par

A ($\sigma$-)structure $\mathfrak{A}$ is composed of
a set $A$, called the universe of $\mathfrak{A}$, equipped with
relations $R_1^{\mathfrak{A}}\subseteq A^{a_1},
\dots, R_m^{\mathfrak{A}}\subseteq A^{a_m}$. When $\sigma$
is understood we may refer to $\sigma$-structures as relational
structures or simply as structures.
A structure is called finite if its universe is a finite set. \par

It is specially relevant the case where $\sigma$ contains a unique
relation $R$ symbol with arity two. In this case two important classes
of relational structures are the class of posets- i.e. those structures
where the relation is anti-symmetric, transitive and anti-reflexive- and 
partially graphs- i.e. those where the relation is symmetric and
anti-reflexive. Unlike posets, one can easily enumerate graphs with a 
given universe size - in other words, number of vertices.

%One can also consider graphs where 'loops' are allowed or directed graphs. 
%Unlike the class of posets, these other classes of graph-like structures share 
%the property that one can easily enumerate their elements up to a given universe 
%size.

### 2019-10-24 Presentacion/Presentación.tex

\AtBeginSection[]
{
	\begin{frame}{Contents}
	\tableofcontents[currentsection]
	\end{frame}
}

@@

\begin{document}
	\frame{\titlepage}
	\frame{\tableofcontents}

	\section{First Order Logic of Sparse Graphs}
	\begin{frame}{The first order language of graphs.}
		\begin{columns}
			\begin{column}{0.55\textwidth}
				\begin{itemize}
					\item Variables $x_1, \dots, x_n, \dots$
					\item Connectives $\wedge, \vee$, equality symbol $=$,
					and negation symbol $\neg$.
					\item Quantifiers $\forall, \exists$.
					\item A binary relation symbol $R$
				\end{itemize}
			\end{column}
			\begin{column}{0.45\textwidth}
				\begin{itemize}
					\item Vertices.
					\item ``And", ``or", ``equals", ``not".
					\item ``For all", ``there exists".
					\item Edges $x\sim y$. 
				\end{itemize}
			\end{column}
		\end{columns}
		~\\
		\[ \forall x_1,x_2 \, R(x_1,x_2) \implies \exists x_3 (\,
		\neg(x_3=x_1)\wedge \neg(x_3=x_2) \wedge R(x_1, x_3))\]
	\end{frame}

@@

	\begin{frame}{Lynch's theorem}
	\begin{theorem}[Lynch, 1992]
		Let $\varphi$ be a sentence in the F.O. language of graphs. 
		Then the map $\mathrm{F}_\varphi: [0,\infty) \rightarrow \R$ given by 
		\[\mathrm{F}_\varphi(\beta)=\Ln \mathrm{Pr}(\, G(n,\beta/n)\models \varphi \,) \]
		is well defined and admits an analytic extension to $\CC$.
	\end{theorem}
	\end{frame}

	\begin{frame}{Overview of the proof}
	Some properties of $G(n,\beta/n)$:
	\\~\\
	\begin{itemize}
		\item The number of cycles of 
		length $3,4\dots, r$
		are asymptotically distributed like independent Poisson 
		variables.
		\item Small cycles are a.a.s far away.
		\item Fixed vertices are a.a.s far away.
		\item The ball of a given radius centered in fixed
		vertex is a.a.s a tree. Any tree occurs with a positive 
		probability.
	\end{itemize}

@@

	\begin{frame}{Overview of the proof}
	For each fixed quantifier rank $k$:
	\\~\\
		\begin{itemize}
			\item[(1)]	It is given a finite classification of "small" uni-cycles.
			\item[(2)]  It is shown that the rank $k$ type of random graph $G$
			 in $G(n,\beta/n)$ a.a.s depends exclusively on the number of "small" uni-cycles
			 belonging to each class. 
			\item[(3)] The asymptotic distribution of those quantities is obtained. 
		\end{itemize}

	\end{frame}
	\section{General relational structures}
	\begin{frame}{Edge sets}
		\begin{definition} Fix
			\begin{itemize}
				\item natural numbers $n,a\in \N$, with $a\geq 2$
				\item a subgroup of the symmetric group $\Phi \leq S_a$
				\item and a subset of pairs $A\subset ([a]\times [a]) \setminus \Delta_a$.
			\end{itemize}
		The \textbf{total edge set} $\mathcal{H}_{(a,\Phi, A)}(n)$ of size $a$, 
		symmetry group $\Phi$ and
		restrictions $A$, on $n$ elements is the set
		\[ \mathcal{H}_{(a,\Phi, A)}(n)= ([n]^a/\Phi) \, \,
		\setminus R, \]
		where
		\[ R = \{\,  [x_1, \dots,x_a] \in [n]^a/\Phi  \, \, 
		| \, \, x_i=x_j \, \text{for some } (i,j)\in A \} \] 
		\end{definition}
	\end{frame}
	\begin{frame}{Graphs}
		\begin{definition}
			An (hyper)-graph $([n], H_1,\dots, H_c)$ with edge colors 
			$1,\dots, c$, sizes $a_1,\dots,a_c$, 
			symmetry groups $\Phi_1,\dots,\Phi_c$ and 
			restrictions $A_1,\dots,A_c$ consists of 
			\begin{itemize}
				\item The vertex set $[n]$ for some natural number $n$.
				\item For $i=1,\dots,c$, a ``colored" edge set $H_i\subseteq \mathcal{H}_{(a_i,\Phi_i,A_i)}(n)$ whose elements 
				have color $i$.
			\end{itemize}
		\end{definition}
	\end{frame}

	\begin{frame}{The first order language}
	Consider the first order purely relational language $\mathcal{L}$ whose signature consists of the relation symbols
	$R_1,\dots, R_c$ with arities $a_1,\dots,a_c$. \\~ \par

@@

	\begin{frame}{The first order language}
		By definition, a graph $G=([n],H_1,\dots, H_n)$ satisfies, for each $1\leq i \leq c$:
		\vspace{0.5 em}
		\begin{itemize}
			\item Symmetry formulas:
			\[ S_g: =\big( R_i(x_1\dots,x_{a_i})\iff R_i(x_{g(1)}\dots,x_{g(a_i)})\big) ,\]
			where $g$ is an element from $\Phi_i$.
			\item Anti-reflexivity formulas:
			\[A_{i,(j,l)}:=\big(R_i(x_1\dots,x_{a_i})\implies 
			\neg(x_j= x_l)\big),\]
			where $(j,l)\in A_i$.
		\end{itemize}

@@

	The random model $HG(n,p_1,\dots, p_c)$ is a discrete probability space where for each graph 
	$G=([n],H_1,\dots,H_c)$,
	\[ \mathrm{Pr}(G)=\prod_{i=1}^{c} p_i^{|H_i|}\cdot (1-p_i)^{|\mathcal{H}_{(a_i,\Phi_i,A_i)}(n)|-|H_i|} . \]
	We consider the case where for each $1\leq i \leq c$,  $p_i(n)=\beta_i/n^{a_i-1}$.
	\\~\\ 
	Let $\beta=(\beta_1,\dots, \beta_c)\in [0,\infty)^c$. We abbreviate
	\[HG(n,p(n,\beta)):= HG(n,\beta_1/n^{a_1-1},\dots, \beta_c/n^{a_c-1}). \]

@@

		\begin{theorem} Let $\varphi$ be a first order sentence in $\mathcal{L}$.
			Then the map $\mathrm{F}:[0,\infty)^c\rightarrow \R$ given by
			\[ \mathrm{F}(\beta_1,\dots, \beta_c)= \Ln 
			\mathrm{Pr}(HG(n,p(n,\beta))\models \varphi )
			\]
			is well defined and admits an analytic extension to $\CC^c$. 
		\end{theorem}

@@

			\begin{equation*}d(x,y)= \min_{\substack{H \leq G\\ 
					H \text{ connected }\\
					x,y\in V(H)}} \big(|V(H)| - 1 \big), \, \, \text{ or } \infty \text{ if }
				x,y \text{ are not connected.}
			\end{equation*}

		\begin{definition} 
			A path between two vertices $x,y$ in a graph $G$ is
			a connected subgraph $H\leq G$ containing both $x,y$ whose
			number of vertices is minimum. 
		\end{definition}

	\end{frame}
	\begin{frame}{Likelihood, trees, cycles and clusters} 
		\begin{definition}
			The likelihood $L(G)$ of a graph $G=(V,H_1,\dots,H_c)$ is
			the number
			\[ |V(G)| - \sum_{i=1}^c |H_i|(a_i-1).\]
		\end{definition}
	~\\
	\end{frame}

@@

	\begin{frame}{The $k$-morphism relation over trees.}
		A rooted $(T,x)$ is a tree $T$ together with a distinguished vertex
		$x\in V(T)$.\par
		\[Tree(y, T) = (T[X], y),\]
		\[\text{where } \, X=\{ z\in V(T) \, | \, d(x,z)=d(x,y)+d(y,z)\}.\]~\\
		The root of an edge $e\in H(T)$ in a rooted tree 
		$(T,x)$ is the vertex $y\in e$ such that $d(x,y)=d(x,e)$.\\~\\
		The radius of an edge $e\in H(T)$ is 
		\[\max_{\substack{y\in e \\ y \text{ not the root of } e}} r(Tree(y,T)). \]

@@

	\begin{frame}{The $k$-morphism relation over trees.}
		Fix $k\in \N$.\\
		We define the $k$-morphism relation over rooted trees of the same radius
		inductively as follows:

		\begin{itemize}
			\item If $r(T_1)=r(T_2)=0$ then $T_1\morph{k} T_2$.
		\end{itemize}
	\end{frame}

	\begin{frame}{The $k$-morphism relation over trees.}
		For $r>0$:
			\begin{itemize}
				\item  First we
				define the type of a en edge with radius less than $r$:

	\begin{frame}{The $k$-morphism relation over trees.}
		\begin{itemize}
		\item If $r(T_1)=r(T_2)=r$ we say that $T_1\morph{K}T_2$ if
		for any edge $k$-type $E$ of radius less than $r$ either:
		\begin{itemize}
			\vspace{0.2 em}
			\item the number of initial edges in $T_1$ and $T_2$ of $k$-type $E$ 
			is the same, or
			\vspace{0.2 em}
			\item both $T_1$ and $T_2$ contain no less than $k+1$
			initial edges of $k$-type $E$. 
		\end{itemize}
		\begin{center}
			\includegraphics[width=0.7\linewidth]{Try.pdf}
		\end{center}

		\end{itemize}

@@

>>>>

%\AtBeginSection[]
%{
%	\begin{frame}{Contents}
%	\tableofcontents[currentsection]
%	\end{frame}
%}

@@

\begin{document}
 \begin{frame}[plain]
	\maketitle
	\small
	\begin{center}
	Supervisor: Marc Noy Serrano
	\end{center}
 \end{frame}
%	\frame{\tableofcontents}

%	\section{First Order Logic of Sparse Graphs}
	\begin{frame}{The first order language of graphs.}
		\begin{columns}
			\begin{column}{0.55\textwidth}
				\begin{itemize}
					\item Variables $x_1, \dots, x_n, \dots$
					\item Connectives $\wedge, \vee$, equality symbol $=$,
					and negation symbol $\neg$.
					\item Quantifiers $\forall, \exists$.
					\item A binary relation symbol $R$
				\end{itemize}
			\end{column}
			\begin{column}{0.45\textwidth}
				\begin{itemize}
					\item Vertices.
					\item ``And", ``or", ``equals", ``not".
					\item ``For all", ``there exists".
					\item Edges $x\sim y$. 
				\end{itemize}
			\end{column}
		\end{columns}
		~\\
		\[ \forall x_1,x_2 \, R(x_1,x_2) \implies \exists x_3 (\,
		\neg(x_3=x_1)\wedge \neg(x_3=x_2) \wedge R(x_1, x_3))\]
	\end{frame}

@@

	\begin{frame}{Lynch's theorem}
	\begin{theorem}[Lynch, 1992]
		Let $\varphi$ be a sentence in the F.O. language of graphs. 
		Then the map $\mathrm{F}_\varphi: [0,\infty) \rightarrow \R$ given by 
		\[\mathrm{F}_\varphi(\beta)=\Ln \mathrm{Pr}(\, G(n,\beta/n)\models \varphi \,) \]
		is well defined and is analytic with respect to $\beta$.
	\end{theorem}
	\end{frame}

	\begin{frame}{Overview of the proof}
	Some properties of $G(n,\beta/n)$:
	\\~\\
	\begin{itemize}
		\item The number of cycles of 
		length $3,4\dots, r$
		are asymptotically distributed like independent Poisson 
		variables.
		\vspace{0.5em}
		\item Small cycles are a.a.s. far away.
		\vspace{0.5em}
		\item Fixed vertices are a.a.s. far away.
		\vspace{0.5em}
		\item The ball of a given radius centered in fixed
		vertex is a.a.s. a tree. Any tree occurs with a positive 
		probability.
	\end{itemize}

@@

	\begin{frame}{Overview of the proof}
	For each fixed quantifier rank $k$:
	\\~\\
		\begin{itemize}
			\item[(1)]	It is given a finite classification of "small" uni-cycles.
			\vspace{0.5em}
			\item[(2)]  It is shown that the rank $k$ type of random graph $G$
			 in $G(n,\beta/n)$ a.a.s. depends exclusively on the number of "small" uni-cycles
			 belonging to each class. 
			\vspace{0.5em}
			\item[(3)] The asymptotic distribution of those quantities is obtained. 
		\end{itemize}
	\end{frame}

%	\section{General relational structures}
	\begin{frame}{Edge sets}
		\begin{definition}
		The \textbf{total edge set} $\mathcal{H}_{(a,\Phi, A)}(n)$ of \textbf{size} $a$, 
		\textbf{symmetry group} $\Phi$ and
		\textbf{restrictions $A$}, on $n$ \textbf{elements} is the set
		\[ \mathcal{H}_{(a,\Phi, A)}(n)= ([n]^a/\Phi) \, \,
		\setminus R, \]
		where
		\[ R = \{\,  [x_1, \dots,x_a] \in [n]^a/\Phi  \, \, 
		| \, \, x_i=x_j \, \text{for some } (i,j)\in A \} \] 
		\end{definition}
	\end{frame}
	\begin{frame}{Graphs}
		\begin{definition}
			An \textbf{(hyper)-graph} $([n], H_1,\dots, H_c)$ with edge colors 
			$1,\dots, c$, sizes $a_1,\dots,a_c$, 
			symmetry groups $\Phi_1,\dots,\Phi_c$ and 
			restrictions $A_1,\dots,A_c$ consists of 
			\begin{itemize}
				\vspace{1em}
				\item The \textbf{vertex set} $[n]$ for some natural number $n$.
				\vspace{1em}
				\item For $i=1,\dots,c$, a ``colored" \textbf{edge set} $H_i\subseteq \mathcal{H}_{(a_i,\Phi_i,A_i)}(n)$ whose elements 
				have color $i$.
			\end{itemize}
		\end{definition}
	\end{frame}

	\begin{frame}{The first order language}
	Consider the first order purely relational language $\mathcal{L}$ with relation symbols
	$R_1,\dots, R_c$ with arities $a_1,\dots,a_c$. \\~ \par

@@

	\begin{frame}{The first order language}
		A graph $G=([n],H_1,\dots, H_n)$ satisfies, for each $1\leq i \leq c$:
		\vspace{0.5 em}
		\begin{itemize}
			\item \textbf{Symmetry formulas}:
			\[ S_g: =\big( R_i(x_1\dots,x_{a_i})\iff R_i(x_{g(1)}\dots,x_{g(a_i)})\big) ,\]
			where $g$ is an element from $\Phi_i$.
			\item \textbf{Anti-reflexivity formulas}:
			\[AR_{i,(j,l)}:=\big(R_i(x_1\dots,x_{a_i})\implies 
			\neg(x_j= x_l)\big),\]
			where $(j,l)\in A_i$.
		\end{itemize}

@@

	The random model $HG(n,p_1,\dots, p_c)$ is a discrete probability space where for each graph 
	$G=([n],H_1,\dots,H_c)$,
	\\~\\
	\[ \mathrm{Pr}(G)=\prod_{i=1}^{c} p_i^{|H_i|}\cdot (1-p_i)^{|\mathcal{H}_{(a_i,\Phi_i,A_i)}(n)|-|H_i|} . \]
	~\\~\\
	We consider the \textbf{sparse} case where for each $1\leq i \leq c$,  $p_i(n)=\beta_i/n^{a_i-1}$.

@@

		\begin{theorem} Let $\varphi$ be a first order sentence in $\mathcal{L}$.
			Then the map $\mathrm{F}:[0,\infty)^c\rightarrow \R$ given by
			\[ \mathrm{F}(\beta_1,\dots, \beta_c)= \Ln 
			\mathrm{Pr}(HG(n,p(n,\beta))\models \varphi ),
			\]
			where 	
			\[p(n,\beta):= (\beta_1/n^{a_1-1},\dots, \beta_c/n^{a_c-1}) \]
			is well defined and is analytic with respect to $\beta=(\beta_1,\dots,\beta_c)$. 
		\end{theorem}

@@

			\begin{equation*}d(x,y)= \min_{\substack{H \leq G, x,y\in V(H)\\ 
					H \text{ connected}}}
					 \big(|V(H)| - 1 \big), \, \, \text{ or } \infty \text{ if }
				x,y \text{ are not connected.}
			\end{equation*}
			\vspace{-0.3em}
		\begin{definition} 
			A path between two vertices $x,y$ in a graph $G$ is
			a minimal graph among the 
			connected subgraphs $H\leq G$ containing both $x,y$.
		\end{definition}
			\begin{center}
			\includegraphics[width=0.8\linewidth]{Path.pdf}
		\end{center}
	\end{frame}
	\begin{frame}{Likelihood, trees, cycles and clusters} 
		\begin{definition}
			The likelihood $L(G)$ of a graph $G=(V,H_1,\dots,H_c)$ is
			the number
			\[ |V(G)| - \sum_{i=1}^c |H_i|(a_i-1).\]
		\end{definition}

@@

%	\begin{frame}{The $k$-morphism relation over trees.}
%		A rooted $(T,x)$ is a tree $T$ together with a distinguished vertex
%		$x\in V(T)$.\par
%		\[Tree(y, T) = (T[X], y),\]
%		\[\text{where } \, X=\{ z\in V(T) \, | \, d(x,z)=d(x,y)+d(y,z)\}.\]~\\
%		The root of an edge $e\in H(T)$ in a rooted tree 
%		$(T,x)$ is the vertex $y\in e$ such that $d(x,y)=d(x,e)$.\\~\\
%		The radius of an edge $e\in H(T)$ is 
%		\[\max_{\substack{y\in e \\ y \text{ not the root of } e}} r(Tree(y,T)). \]
%		
%	\end{frame}

	\begin{frame}{The $k$-morphism relation over trees.}
		Fix $k\in \N$.\\
		We define the $k$-morphism relation over rooted trees of the same radius
		inductively as follows:
		\\~\\~\\
		\begin{itemize}
			\item If $r(T_1)=r(T_2)=0$ then $T_1\morph{k} T_2$.
		\end{itemize}
	\end{frame}

	\begin{frame}{The $k$-morphism relation over trees.}
		If $r(T_1)=r(T_2)>0$:
			\begin{itemize}
				\item  First we
				define the $k$-type of a an initial edge:

	\begin{frame}{The $k$-morphism relation over trees.}
		\begin{itemize}
		\item We say that $T_1\morph{k}T_2$ if
		for any defined edge $k$-type $E$ either:
		\begin{itemize}
			\vspace{0.2 em}
			\item the number of initial edges in $T_1$ and $T_2$ of $k$-type $E$ 
			is the same, or
			\vspace{0.2 em}
			\item both $T_1$ and $T_2$ contain no less than $k+1$
			initial edges of $k$-type $E$. 
		\end{itemize}
		\begin{center}
			\includegraphics[width=0.7\linewidth]{Try.pdf}
		\end{center}

		\end{itemize}
	\end{frame}
%
%	\begin{frame}{The $k$-morphism relation for graphs}
%		To make the definitions suitable for proofs using E.F. games we need to work with "graphs
%		with constants". 
%		\begin{definition}
%			The center of a connected graph $G(\clist)$ is its minimal 
%			connected subgraph containing all the constants and clusters.\\
%			\vspace{0.2 em} If $G(\clist)$
%			is not connected its center is the union of the centers of its connected
%			components.   
%		\end{definition}
%	\end{frame}
%
%		
%	\begin{frame}{The $k$-morphism relation for graphs}
%	A sketch of a center:
%	\begin{center}
%		\includegraphics[width=0.5\linewidth]{Center.pdf}
%	\end{center}
%	\end{frame}
%
%	\begin{frame}{The $k$-morphism relation for graphs}
%	\begin{definition} 
%		We say that $G_1(\clist)\morph{k}G_2(\clist)$, if there is an isomorphism
%		$f:Center(G_1)\rightarrow Center(G_2)$ s.t.
%		\begin{itemize}
%			\item $f(c^1_i)=c^2_i$ for all constants, and
%			\item $Tree(x,G_1)\morph{k} Tree(f(x),G_2)$ for all $x\in V(Center(G_1))$.
%		\end{itemize}
%	\end{definition}

	\begin{frame}{The $k$-morphism relation for uni-cycles}
	\begin{definition} 
		Let $G_1,G_2$ be uni-cycles. Let $O_1, O_2$ be their cycles respectively.\\
		 $G_1\morph{k}G_2$, if  for some $f$: \\~\\
		\begin{itemize}

			\item $O_1 \morph{f} O_2$, and \\~\\

			\item $Tree(x,G_1)\morph{k} Tree(f(x),G_2)$ for all $x\in V(O_1)$.
		\end{itemize}
	\end{definition}
	\end{frame}
%	
%	\end{frame}
%	
	\begin{frame}{The $k$-morphism relation for uni-cycles}
	\begin{center}
		\includegraphics[width=0.95\linewidth]{KmorphicCycles1.pdf}
	\end{center}
	\end{frame}

	\begin{frame}{The $k$-morphism relation for uni-cycles}
	\begin{center}
		\vspace{0.48 em}
		\includegraphics[width=0.95\linewidth]{KmorphicCycles2.pdf}
	\end{center}
	\end{frame}

	\begin{frame}{The $k$-morphism relation for uni-cycles}
	\begin{center}
	\vspace{2.3em}
	\includegraphics[width=\linewidth]{KmorphicCycles3.pdf}
	\end{center}
	\end{frame}

	\begin{frame}{The $k$-morphism relation for cycles}

		Uni-cyclic $k$-morphic graphs have the same
		first order rank $k$-type.	\\~\\

		The tool for proving this are \textbf{Ehrenfeucht Fraisse games}.
		\\~\\

		The $k$-morphism relation gives, for any $r$, a \textbf{finite classification} of the cycles of diameter
		at most $r$ with trees of radii at most $r$ hanging from their vertices.

@@

	\begin{frame}{The landscape of $HG(n,p(n,\beta))$}
		\begin{itemize}
		\item Clusters with diameter at most $d$, for any fixed $d$, a.a.s. will not appear.
		In particular, small cycles are a.a.s. far away.
	\end{itemize}
	\begin{center}
			\includegraphics[width=0.8\linewidth]{FarCycles.pdf}
	\end{center}

@@

	\begin{frame}{The landscape of $HG(n,p(n,\beta))$}
	\begin{itemize}
		\item Given any fixed cycles $O_1, \dots, O_l$, their quantities converge
		in distribution to independent Poisson 
		variables.
		\vspace{1em}
		\item Fixed vertices are a.a.s. far away.
		\vspace{1em}
		\item The ball of a given radius centered in fixed
		vertex is a.a.s. a tree. Any tree occurs with a positive 
		probability.
	\end{itemize}
	~\\
	In consequence, F.O. properties of a fixed quantifier rank $k$ only depend on the small neighbourhoods of the small cycles in
	a graph.  
	\end{frame}

	\begin{frame}{Probabilities of uni-cycles}

	The main tool for computing probabilities is the following:

		\begin{theorem}{(Multivatiate Brun's Sieve)}
			For $1\leq i \leq l$ let $\{X_i(n)\}_{n\in \N}$,  be successions of 
			random variables s.t the $X_i(n)$'s are sums of random indicator variables.
			If for any natural numbers $a_1,\dots, a_l$
			\[ \Ln E\left[\prod_{i=1}^l \binom{X_i}{a_i} \right] = 
			\prod_{i=1}^l \frac{\lambda_i^{a_i}}{a_i!}, \]
			then
			\[ \forall x_1,\dots, x_l\in \N: \quad \Ln \mathrm{Pr}(\wedge_{i=1}^l
			X_i=x_i)= \prod_{i=1}^l \mathrm{Poiss}_{\lambda_i}(x_i).\]

		\end{theorem}

	\begin{frame}{Ending summary}
		\begin{itemize}
			\item $HG(n,p(\beta,n))$ is very similar to $G(n,\beta/n)$. The ideas behind Lynch's proof
			can be used here after finding suitable definitions. 
			\\~\\
			\item The main increase in complexity is due to the fact that trees are more complicated in $HG(n,p(\beta,n))$:
			the types of the edges have to be considered now. 
			\\~\\
			\item Using Brun's Sieve simplifies the harder combinatorial proofs.  
		\end{itemize}
	\vfill
	\pause
	{\hfill \Large Thank you for attention!}
 	\end{frame}
